Topology and experimental distinguishability

### 2018-12-12 Articles/TopologyAndExperimentalDistinguishability/article-topologyproceedings.tex
Minor changes after acceptance

\begin{rem}
	Experimental observations are not closed under negation. The existence of an experimental test to verify a statement does not imply the existence of an experimental test to verify its negation.
\end{rem}

@@

As experimental relationships are themselves distinguishable, we can recursively form experimental relationships between experimental relationships leading to functions of arbitrary order while remaining within the definitions provided. The framework is therefore complete.

@@

In light of this work, the effectiveness of mathematics in the natural sciences is perhaps not so unreasonable. We hope that the methods and results shown here can provide a more solid foundation to formalize experimental sciences.

@@

	\bibitem{russell} B. Russell, {\it The problems of philosophy}, Home University Library, 1912.
\end{thebibliography}

>>>>

\begin{rem}
	Experimental observations are not closed under negation. The existence of an experimental test to verify a statement does not imply the existence of an experimental test to verify its negation.\footnote{Continuing the example, finding a black swan constitutes proof that black swans exist while not finding any black swans does not constitute proof that black swans do not exist.}
\end{rem}

@@

As experimental relationships are themselves distinguishable, we can recursively form experimental relationships between experimental relationships leading to functions of arbitrary order while remaining within the definitions provided. The framework is therefore closed.

@@

In light of this work, the effectiveness of mathematics in the natural sciences is perhaps not so unreasonable. We hope that the methods and results shown here can provide a more solid foundation to formalize experimental sciences.\footnote{For the latest developments in our effort to provide a more solid mathematical foundations to experimental sciences see \cite{Book}}

@@

	\bibitem{russell} B. Russell, {\it The problems of philosophy}, Home University Library, 1912.

	\bibitem{Book} G. Carcassi, C. A. Aidala: Assumptions of Physics (in preparation). http://assumptionsofphysics.org/book/, Ann Arbor, MI, USA, 2018.
\end{thebibliography}
